### 2020-08-24 sections/experience.tex
Update experience.tex

\begin{cventries}
\cventry
{Instructor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2018 - on leave}
{Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}

@@

\cventry
{Adjunct Professor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2014 - 2017}
{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}

>>>>

\begin{cventries}
\cventry
{Instructor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2019 - on leave}
{Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}

\cventry
{Adjunct Professor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2014 - 2018}
{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}

@@

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, Chile} 
{2013 - 2016}
{School of Government and Public Management, Institute for Public Affairs}\vspace{1.5mm}
